
%%%%%
% To do all:
% VisIt footnote, I-NERI->INERI, cross-(!)section, exact Re&Reh, Specs citation/table? Fig->Figure, MYRRHA

\documentclass[11pt]{anlreport}

\usepackage{booktabs}
\usepackage[shortcuts]{glossaries}

\input preambl_anl

%\usepackage[title,titletoc]{appendix}	%?
%\renewcommand{\appendixname}{Appendix}
%%\usepackage[toc,page]{appendix}
%\usepackage{sectsty}   % for smaller chapter/appendix
%\chapternumberfont{\fontsize{12}{14}\selectfont}  % for 11pt option with \chapter/Appendix?
%\chaptertitlefont{\fontsize{12}{14}\selectfont}

%\renewcommand{\bibname}{References}

\title{Initial full core SMR simulations with NekRS}

\author[1,2]{\rm Elia Merzari}
\author[2]{Jun Fang}
\author[2]{Dillon Shaver}
\author[3]{Yu-Hsiang Lan}
\author[3]{Misun Min}
\author[3]{Paul Fischer}
\author[4]{Ronald Rahaman}
\author[4]{Paul Romano}

\affil[1]{Nuclear Engineering Department, Pennsylvania State University}
\affil[2]{Nuclear Science and Engineering Division, Argonne National Laboratory}
\affil[3]{Mathematics and Computer Science Division, Argonne National Laboratory}
\affil[4]{Computational Science Division, Argonne National Laboratory }

\date{October 1, 2020}
\division{Nuclear Science and Engineering Division}
\building{208}
\reportNumber{ANL-20/72}

\begin{document}

\clearpage
\thispagestyle{empty}
\pagenumbering{roman}
\tableofcontents
\clearpage
\listoffigures
\listoftables
\newpage
\printglossary
\newpage

%% =========
\graphicspath{{./Figs/}}

\input execsum

\addcontentsline{toc}{section}{Executive Summary}
\newpage
\pagenumbering{arabic}
\setcounter{page}{1}
%\counterwithout{section}{chapter}  % \usepackage{chngcntr} %?

%% =========

\section{Introduction}

The ExaSMR project is developing tools for coupling \acf{mc} radiation
transport solvers to a \acf{cfd} solver.  Work is based on the Shift MC, OpenMC MC, and Nek5000/NekRS CFD codes. The application development objective is to optimize these applications for exascale execution of full core simulations and modularize and integrate them into a common framework for coupled and individual execution. The work is supported by secondary applications for data processing and third-party libraries.

Given the sheer scale of nuclear systems, the main algorithmic driver on the CFD side is weak scaling.
The focus for the first four years is  on demonstrating scaling up to a full reactor core for high-fidelity simulation of turbulence. The goal is to demonstrate full-core fluid calculations aimed at better predicting the steady-state performance. The first step is performing URANS calculations, after which analysis will be conducted with zonal hybrid LES-RANS that provides an additional scaling dimension besides the number of assemblies. LES may be used to simulate a portion of a core, while the remainder will be handled by RANS.

A key aspect of the modeling of PWR fuel assemblies is the presence of spacer grids and the mixing promoted by mixing vanes or equivalents. In the case of fine-scale LES simulations, the grids can be modeled explicitly. In our URANS simulations we used a reduced order methodology based on momentum sources to mimic the mixing of the vanes (see for example Capone et al. \cite{Capone2016}). The momentum sources have been carefully calibrated with detailed LES simulations of spacer grids performed with Nek5000.

In previous milestones for the ExaSMR project we have focused on assembly level simulations with Nek5000 to assess baseline performance \cite{merzari2018performance} \cite{merzari2020wall}. We now shift focus to full core simulations. In fact, \textit{this milestone provides the first full-core pin resolved simulations ever performed to our knowledge}. \textbf{This represents a significant advancement in capability for the CFD of nuclear reactors}.

This has been made possible by the CEED and ExaSMR investment in a novel port of Nek5000 called NekRS. NekRS was released in 2018 and it is developing rapidly, with significant improvements in performance \cite{merzari2020toward}. All large-scale simulations performed here have been conducted on the Summit supercomputer.

As a first step we briefly discuss the status of NekRS and some recent code improvements performed in collaboration with CEED (Section~\ref{sec:nekrs}).   Then we discuss the development of the momentum source models (Section~\ref{sec:msm}) and the calibration procedure used. The methodology will need to be further extended and tested on more grids, but it shows a great deal of potential for the type of analysis presented here. We then discuss a series of full core analyses that have been performed as part of this study and the related numerical setups (Section~\ref{sec:model}). In the results section we discuss selected outcomes of the simulation campaigns performed including some performance results (Section~\ref{sec:results}). The results section includes an updated FOM measurement. Finally some conclusions are discussed.

We reiterate  that the work presented here was performed in close collaboration with the CEED project.
%%---------------------------------------------------------------------------%%
\input{nekrs.tex}
\input{msm.tex}
\input{problem.tex}
\input{results.tex}
\input{conclusions.tex}



%\clearpage

\section*{Acknowledgments}
\addcontentsline{toc}{section}{Acknowledgments}

This research was supported by the Exascale Computing Project (ECP), Project
Number: 17-SC-20-SC, a collaborative effort of two DOE organizations---the
Office of Science and the National Nuclear Security Administration---responsible
for the planning and preparation of a capable exascale ecosystem---including
software, applications, hardware, advanced system engineering, and early testbed
platforms---to support the nation's exascale computing imperative. This research
used resources of the Oak Ridge Leadership Computing Facility at the Oak Ridge
National Laboratory, which is supported by the Office of Science of the U.S.
Department of Energy under Contract No. DE-AC05-00OR22725.


%\afterpage{\clearpage}
\pagebreak

\bibliographystyle{unsrt}
%% =========
\bibliography{references}
\addcontentsline{toc}{section}{References}

\newpage
%%\usepackage[toc,page]{appendix}	%?
%%\usepackage[toc]{appendix}
%\appendix
%\renewcommand\thesection{Appendix \Alph{section}}
%%
%\section{Other PLANDTL Figures}
%\addcontentsline{toc}{section}{Other PLANDTL Figures}

%\input appx %?

%\includepdf[pages=-]{rep_61specs_not.pdf}


\newpage
%\endpage

\end{document}
