%%---------------------------------------------------------------------------%%
%% report.tex
%% Tom Evans
%% Wednesday January 4 13:31:55 2017
%% Copyright (C) 2008-2017 Oak Ridge National Laboratory, UT-Battelle, LLC.
%%---------------------------------------------------------------------------%%

% Add the 'draft' option to compile faster (without images e.g.)
%\documentclass[draft]{ecpreport}
\documentclass{ecpreportv2}
\usepackage[binary-units,per-mode=symbol-or-fraction]{siunitx}
\usepackage{multirow}
\usepackage{float}
\usepackage[shortcuts]{glossaries}
\usepackage{algorithm}          % Provides algorithm environment
\usepackage{algorithmicx}       % Provides algorithmic block
\usepackage{algpseudocode}      % Option of algorithmicx package
\usepackage{caption}
\usepackage{subcaption}
\usepackage{cite}
\usepackage[nameinlink,capitalize]{cleveref}


\renewcommand{\sectionautorefname}{\S}
\renewcommand{\subsectionautorefname}{\S}
\renewcommand{\subsubsectionautorefname}{\S}
\renewcommand{\equationautorefname}{Eq.}

\newcommand{\iso}[2][]{\ensuremath{\left.^{\text{{#2}}}\text{{#1}}\right.}}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{P}{S[round-mode=places,round-precision=4,
                    table-format=-1.4e-2,output-exponent-marker=\text{e}]}
\newcolumntype{Q}{S[round-mode=places,round-precision=3,
                    table-format=-1.3e-1,output-exponent-marker=\text{e}]}


\let\DeclareUSUnit\DeclareSIUnit
\let\US\SI
\DeclareUSUnit\inch{in}
\DeclareUSUnit\psia{psia}
\DeclareSIUnit\src{source}

\newcommand{\milestone}[1]{\href{https://jira.exascaleproject.org/projects/ADSE08/issues/#1}{#1}}

%%---------------------------------------------------------------------------%%
%% VARIABLES
%%---------------------------------------------------------------------------%%
\author{
  Elia Merzari, ANL, PSU
  \and Jun Fang, ANL
  \and Dillon Shaver, ANL
  \and Misun Min, ANL
  \and Paul Fischer, ANL
  \and Yu-Hsinag Lan, ANL
  \and Ronald Rahaman, ANL
  \and Paul Romano, ANL
}
\title{Initial full core SMR simulations with Nek5000 and NekRS}
\date{\today}
\wbs{XXX}
\id{XXX}
\reportnum{ECP-U-2020-XXX}

\submitter{Elia Merzari}

\concurrence{Steve Hamilton}
\concurrenceorg{Oak Ridge National Laboratory}

\concurrence{Thomas Evans}
\concurrenceorg{Oak Ridge National Laboratory}

\approver{Andrew Siegel}
\approverorg{Argonne National Laboratory}

\setacronymstyle{long-short}
\makeglossaries
\input{glossary}

% US units
\let\DeclareUSUnit\DeclareSIUnit
\let\US\SI
\DeclareUSUnit\inch{in}

%%---------------------------------------------------------------------------%%
%% FRONT MATTER
%%---------------------------------------------------------------------------%%

\begin{document}
\frontmatter

%%---------------------------------------------------------------------------%%
%% REVISION LOG

\begin{revlog}
  1.0 & \today & Original & \\\hline
\end{revlog}

%%---------------------------------------------------------------------------%%
% EXECUTIVE SUMMARY

\begin{abstract}

This document describes the completion of ExaSMR milestone ``Full core simulations'' (JIRA ID \milestone{ADSEXX}).  As part of this milestone for the first a novel set of pin-resolved computational fluid dynamics (\ac{cfd}) full-core simulations have been performed. These simulations represent a significant increase in capability in what is now possible with \ac{cfd} on pre-Exascale systems. The simulations have been performed with the spectral element solvers Nek5000 and NekRS on the supercomputer Summit. The simulations show a sequence of increasing modeling complexity: (1) LES simulations in bare bundle, (2) RANS simulations in bare bundles, (3) RANS simulations with momentum sources and (4) conjugate heat transfer calculations.

\end{abstract}

\tableofcontents
\listoffigures
\listoftables
\newpage
\printglossary

%%---------------------------------------------------------------------------%%
% MAIN DOCUMENT
%%---------------------------------------------------------------------------%%

\mainmatter
\section{Introduction}

The ExaSMR project is developing tools for coupling \acf{mc} radiation
transport solvers to a \acf{cfd} solver.

%%---------------------------------------------------------------------------%%

\input{nekrs.tex}
\input{msm.tex}
\input{problem.tex}
\input{results.tex}
\input{conclusions.tex}

%%---------------------------------------------------------------------------%%
\section*{Acknowledgments}

This research was supported by the Exascale Computing Project (ECP), Project
Number: 17-SC-20-SC, a collaborative effort of two DOE organizations---the
Office of Science and the National Nuclear Security Administration---responsible
for the planning and preparation of a capable exascale ecosystem---including
software, applications, hardware, advanced system engineering, and early testbed
platforms---to support the nation's exascale computing imperative. We gratefully
acknowledge the computing resources provided by the Joint Laboratory for System
Evaluation at Argonne National Laboratory. This research used resources of the
Oak Ridge Leadership Computing Facility at the Oak Ridge National Laboratory,
which is supported by the Office of Science of the U.S. Department of Energy
under Contract No. DE-AC05-00OR22725.

%%---------------------------------------------------------------------------%%
%% References

\bibliographystyle{unsrt}
\bibliography{references}

%%---------------------------------------------------------------------------%%
%% APPENDICES
%%---------------------------------------------------------------------------%%

\appendix
\input{appendixa.tex}
\input{appendixb.tex}

%%---------------------------------------------------------------------------%%

\end{document}

%%---------------------------------------------------------------------------%%
% end of report.tex
%%---------------------------------------------------------------------------%%
